---
title: "Meta data for location data"
author: "Anthony Davidson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
#libraries
library(rgdal)
library(tidyverse)
library(ggplot2)

#knitting options
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
usa_cities <- readRDS("../data/usa_cities.rds")
all_cities <- readRDS("../data/cities.rds")

# data from mymaps google

```

## RDS file structure

```{r}
kableExtra::kable(head(usa_cities))
```

### Importing data from google mymaps

This file comes as a `.kmz` file as [here]("https://www.google.com.au/maps/d/u/0/embed?mid=1DAgemW-rkdMHTO8fxnbvbSVF4H0XNLd_")

### `kmz` conversion

We need to convert the my-maps data from a zipped `kml` file that is stored as the `kmz` file downloaded from mymaps data. \newline
Follow these steps [currently not working]:

1. Download data
2. Add `.zip` to `.kml` file
3. Unzip renamed file (as per normal in windows)
4. Change the file extention to `kmz`
5. Import correct file sections using the following code:

### Running code

```{r}
##librares needed
library(rgdal)
library(tidyverse)
library(ggplot2)
library(sf)
```

```{r eval=FALSE, include=FALSE}
sharks <- readOGR("./data/shark-sites-sightings.kmz") 

sharks
```

## Splitting data

Grids (polygons) and abundance is points!!

```{r}
res.one.grids <- readOGR("./data/i-esearch.kml", require_geomType=c("wkbPolygon")) 

res.one.points <- readOGR("./data/i-esearch.kml", require_geomType=c("wkbPoint")) 
```

```{r}
file <- "./data/i-esearch.kml"
nc <- st_read(dsn = file, quiet = TRUE)
# limit to first 2 counties
nc <- nc[1:2,]
# convert to SpatialPolygonsDataFrame
nc_sp <- as(nc, "Spatial")
```

```{r}
# mod data for tidyverse and lat/longs
library(tidyverse)
library(leaflet)
# convert res.one.points to tibble for easy mucking around
res.one.points %>%
  class()

res.one.points$Name
res.one.points$Description

dat <- as.data.frame(res.one.points[1][,1])

dat1 <- dat %>%
  mutate(lng = coords.x1,
         lat = coords.x2) %>%
    select(lng, lat, Name)

str(dat1)
# #make one of those for fun
#  # SpatialPointsDataFrame(res.one.points[,c("lng", "lat")], res.one.points)
# require(stringr)
# 
# 
# variable <- c(paste0("A", c(rep(1, 4), rep(2, 3))),
#               paste0("B", rep(1, 4))
#               )
# 
# data.frame(
#     treatment = str_extract(variable, "[[:alpha:]]"),
#     time = as.numeric(str_extract(variable, "[[:digit:]]"))
#     )
# 
# # %>%
#   extract(coordinates, into = c("lat", "long"), regex = "([+]+)([-]+)")

```

Now to add data to map:

```{r fig.height=12, fig.width=7}
m3 <- leaflet(quakes) %>%
        addProviderTiles("Stamen.Toner") %>%
        addMarkers(lat = dat1$lat, lng = dat1$lng)
m3
```



```{r eval=FALSE, include=FALSE}
# import jsosn data from leaflet
# instructions here...


# From http://leafletjs.com/examples/choropleth/us-states.js
# Data Referenced from https://github.com/rstudio/leaflet/tree/master/docs/json/
states <- geojsonio::geojson_read("./json/us-states.geojson", what = "sp")
bins <- c(0, 10, 20, 50, 100, 200, 500, 1000, Inf)
pal <- colorBin("YlOrRd", domain = states$density, bins = bins)
labels <- sprintf(
  "<strong>%s</strong><br/>%g people / mi<sup>2</sup>",
  states$name, states$density
) %>% lapply(htmltools::HTML)
leaflet(states) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  addPolygons(
    fillColor = ~pal(density),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlight = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~density, opacity = 0.7, title = NULL,
    position = "bottomright")
```


## Extracting mymaps data

This is for security reasons.

Dont forget to unzip `kmz` file from `mymaps` so we can use the following code:

### First

- rename BikePaths.kmz to BikePaths.kml.zip
- unzip this file
- read the unzipped file with st_read("doc.kml")

I think that reading .kmz (i.e.. zipped .kml's) files requires libkml (which your gdal lib doesn' t have), and that the kml driver (not the libkml driver) only reads .kml.

```{r}
sharks <- readOGR("./data/ssightings.kml") 

sharks
```

## Splitting data

Grids (polygons) and abundance is points!!

```{r}
res.one.grids <- readOGR("./data/research.kml", require_geomType=c("wkbPolygon")) 

res.one.points <- readOGR("./data/research.kml", require_geomType=c("wkbPoint")) 
```
But its not correct...

```{r}
file <- "./data/research.kml"
nc <- st_read(dsn = file, quiet = TRUE)
# limit to first 2 counties
nc <- nc[1:2,]
# convert to SpatialPolygonsDataFrame
nc_sp <- as(nc, "Spatial")
```

```{r}
# mod data for tidyverse and lat/longs
library(tidyverse)

# convert res.one.points to tibble for easy mucking around
res.one.points %>%
  class()

res.one.points$Name
res.one.points$Description

dat <- as.data.frame(res.one.points[1][,1])

dat1 <- dat %>%
  mutate(lng = coords.x1,
         lat = coords.x2) %>%
    select(lng, lat, Name)

str(dat1)
# #make one of those for fun
#  # SpatialPointsDataFrame(res.one.points[,c("lng", "lat")], res.one.points)
# require(stringr)
# 
# 
# variable <- c(paste0("A", c(rep(1, 4), rep(2, 3))),
#               paste0("B", rep(1, 4))
#               )
# 
# data.frame(
#     treatment = str_extract(variable, "[[:alpha:]]"),
#     time = as.numeric(str_extract(variable, "[[:digit:]]"))
#     )
# 
# # %>%
#   extract(coordinates, into = c("lat", "long"), regex = "([+]+)([-]+)")

```

Now to add data to map:

```{r}
m3 <- leaflet(quakes) %>%
        addProviderTiles("Stamen.Toner") %>%
        addMarkers(lat = dat1$lat, lng = dat1$lng)
m3
```

```{r}
# a different approach
# following blog better this makes more sense

#data.frame core data
dat$lng
dat1$lng
dat1$Name

```

```{r}
#simple steps...
# 1. add data to mymaps datasets

```

